|

### 2023-08-18 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
a little bit more writing

To most of us, we likely do not trust this as a basis to infer partisanship as other forms of information such as whether a potential neighbor is displaying a political yard sign. However, these usually only show up every couple of years during the election season and are displayed by those who tend to be highly politically active -- so, they are not universally displayed [@makse_politics_2019]. Absent explicit information about the partisan composition, we might be willing to accept that the information we are basing our inferences on as

>>>>

To most of us, we likely do not trust this as a basis to infer partisanship as other forms of information such as whether a potential neighbor is displaying a political yard sign. However, these usually only show up every couple of years during the election season and are displayed by those who tend to be highly politically active -- so, they are not universally displayed [@makse_politics_2019]. Additionally, other decisions such as the color of the house are determined by Homeowners Associations (HOAs). The choices of car colors are less constrained by other external factors. So, we may reasonably assume that if we see a neighborhood with a significant number of red cars, we may assume that the local sports team color must be red. However, if we are searching for cues toward the partisan composition of the neighborhood, we may then assume that the neighborhood has a large number of Republicans, whether that is accurate or not.
